### 2020-07-06 README.Rmd
Build README

```{r, eval=FALSE}
load("model_comp_tbl_4_shuffles.RData")
model_comp <- bind_rows(
  model_comp_tbl %>% select(species_notion, run_time, observed = observed_RMSE, shuffle = shuffle_RMSE) %>% mutate(CV = FALSE),
  model_comp_tbl %>% select(species_notion, run_time, observed = observed_RMSE_CV, shuffle = shuffle_RMSE_CV) %>% mutate(CV = TRUE)
) %>%
  gather(type, RMSE, -c(species_notion, run_time, CV)) %>%
  arrange(CV, model_number) %>%
  mutate(
    species_notion = case_when(
      species_notion == "trait_group" ~ "1. Trait-based (6): lambda = 6 x 6",
      species_notion == "family" ~ "2. Phylogenetic family (20): lambda = 20 x 20",
      species_notion == "species" ~ "3. Actual species (36): lambda = 36 x 36"
    )
  )

>>>>

```{r, eval=TRUE}
load("2020-06-25_model_comp_tbl_49_shuffles.RData")
model_comp <- bind_rows(
  model_comp_tbl %>% select(species_notion, run_time, observed = observed_RMSE, shuffle = shuffle_RMSE) %>% mutate(CV = FALSE),
  model_comp_tbl %>% select(species_notion, run_time, observed = observed_RMSE_CV, shuffle = shuffle_RMSE_CV) %>% mutate(CV = TRUE)
) %>%
  gather(type, RMSE, -c(species_notion, run_time, CV)) %>%
  mutate(
    species_notion = case_when(
      species_notion == "trait_group" ~ "1. Trait-based (6): lambda = 6 x 6",
      species_notion == "family" ~ "2. Phylogenetic family (20): lambda = 20 x 20",
      species_notion == "species" ~ "3. Actual species (36): lambda = 36 x 36"
    )
  ) %>% 
  filter(species_notion != "3. Actual species (36): lambda = 36 x 36")
